Hyperopt-Sklearn: Subtitle?

### 2014-04-26 papers/2014-automl/paper.tex
paper - moved fig:search to sec2

\iffalse   % UNCOMMENT THIS STUFF TO BE MORE SPACE EFFICIENT
\renewcommand\floatpagefraction{.9}
\renewcommand\dblfloatpagefraction{.9} % for two column documents
\renewcommand\topfraction{.9}
\renewcommand\dbltopfraction{.9} % for two column documents
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.1}
\setcounter{totalnumber}{50}
\setcounter{topnumber}{50}
\setcounter{bottomnumber}{50}
\fi

@@

The configuration space we experiment on below includes five preprocessing algorithms and seven classification algorithms.
The full search space is illustrated in Figure~\ref{fig:searchspace}.
The preprocessing algorithms were (by class name, followed by n. hyperparameters + n. unused hyperparameters): \texttt{PCA}(2), \texttt{StandardScaler}(2), \texttt{MinMaxScaler}(1), \texttt{Normalizer}(1), and \texttt{TF-IDF}(0+9).
The first four preprocessing algorithms were for dense features.
PCA performed whitening or non-whitening principle components analysis.
The \texttt{StandardScaler}, \texttt{MinMaxScaler}, and \texttt{Normalizer} did various feature-wise affine transforms to map numeric input features onto values near 0 and with roughly unit variance.
The \texttt{TF-IDF} pre-processing module performed feature extraction from text data.
The classification algorithms were (by class name (used + unused hyperparameters)): \texttt{SVC}(23), \texttt{LinearSVC}(6), \texttt{KNN}(4+5), \texttt{RandomForest}(8), \texttt{ExtraTrees}(8), \texttt{SGD}(8+4), and \texttt{MultinomialNB}(2).
The \texttt{SVC} module is a fork of LibSVM, and our wrapper has 23 hyperparameters because we treated each possible kernel as a different classifier, with its own set of hyperparameters: Linear(4), RBF(5), Polynomial(7), and Sigmoid(6).

In total, our parameterization had 65 hyperparameters: 6 for preprocessing and 59 for classification.
The search space includes 15 boolean variables, 14 categorical, 17 discrete, and 19 real-valued variables.
Although the total number of hyperparameters is large, the number of {\em active} hyperparameters describing any one model is much smaller: a model consisting of \texttt{PCA} and a \texttt{RandomForest} for example,
would have only 12 active hyperparameters (1 for the choice of preprocessing, 2 internal to PCA, 1 for the choice of classifier and 8 internal to the RF).
Hyperopt description language allows us to differentiate between {\em conditional} hyperparameters (which must always be assigned) and {\em non-conditional} hyperparameters (which may remain unassigned when they would be unused).
We make use of this mechanism extensively so that Hyperopt's search algorithms do not waste time learning by trial and error that e.g. RF hyperparameters have no effect on SVM performance.
Even internally within classifiers, there are instances of conditional parameters: \texttt{KNN} has conditional parameters depending on the distance metric,
and \texttt{LinearSVC} has 3 binary parameters (``loss'', ``penalty'', and ``dual'') that admit only 4 valid joint assignments.
We also included a blacklist of (preprocessing, classifier) pairs that did not work together, e.g. PCA and MinMaxScaler were incompatible with MultinomialNB, TF-IDF could only be used for text data, and the tree-based classifiers were not
compatible with the sparse features produced by the TF-IDF preprocessor.
Allowing for a 10-way discretization of real-valued hyperparameters, and taking these conditional hyperparameters into account, a grid search of our search space would still require an infeasible number of evalutions (on the order of $10^{12}$).

@@

%To support the hypothesis that the search carried out by hyperopt-sklearn is necessary for good performance on a range of data sets, we present three pieces of evidence.
%First, looking again at Figure~\ref{fig:avg_test_scores}, note that 
%Figure~\ref{fig:pies} shows that 
%different data sets lead hyperopt-sklearn to select

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{graphics/sklearn_space_all_together}
    \caption{
	    XXX
    }
    \label{fig:space}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=5.00in]{graphics/AverageTestScoresClassifiersTPE}
    \caption{
        For each data set, searching the full configuration space (``Any Classifier'') delivered performance approximately on par with a search that was restricted to the best classifier type.
        (Best viewed in color.)
    }
    \label{fig:avg_test_scores}
%\vspace{-3em}
\end{figure}

>>>>

\iftrue   % UNCOMMENT THIS STUFF TO BE MORE SPACE EFFICIENT
\renewcommand\floatpagefraction{.9}
\renewcommand\dblfloatpagefraction{.9} % for two column documents
\renewcommand\topfraction{.9}
\renewcommand\dbltopfraction{.9} % for two column documents
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.1}
\setcounter{totalnumber}{50}
\setcounter{topnumber}{50}
\setcounter{bottomnumber}{50}
\fi

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{graphics/sklearn_space_all_together}
    \caption{
        Hyeropt-sklearn's full search space (``Any Classifier'') consists of a (preprocessing, classsifier) pair.
        There are 6 possible preprocessing modules and 6 possible classifiers.
        Choosing a model within this configuration space means choosing paths in an ancestral sampling process.
        The highlighted green edges and nodes represent a (PCA, K-Nearest Neighbor) model.
        The number of active hyperparameters in a model is the sum of parenthetical numbers in the selected boxes. For the PCA+KNN combination, 7 hyperparameters are activated.
    }
    \label{fig:space}
\end{figure}
The configuration space we experiment on below includes six preprocessing algorithms and seven classification algorithms.
The full search space is illustrated in Figure~\ref{fig:space}.
The preprocessing algorithms were (by class name, followed by n. hyperparameters + n. unused hyperparameters): \texttt{PCA}(2), \texttt{StandardScaler}(2), \texttt{MinMaxScaler}(1), \texttt{Normalizer}(1), \texttt{None}, and \texttt{TF-IDF}(0+9).
The first four preprocessing algorithms were for dense features.
PCA performed whitening or non-whitening principle components analysis.
The \texttt{StandardScaler}, \texttt{MinMaxScaler}, and \texttt{Normalizer} did various feature-wise affine transforms to map numeric input features onto values near 0 and with roughly unit variance.
The \texttt{TF-IDF} pre-processing module performed feature extraction from text data.
The classification algorithms were (by class name (used + unused hyperparameters)): \texttt{SVC}(23), \texttt{KNN}(4+5), \texttt{RandomForest}(8), \texttt{ExtraTrees}(8), \texttt{SGD}(8+4), and \texttt{MultinomialNB}(2).
The \texttt{SVC} module is a fork of LibSVM, and our wrapper has 23 hyperparameters because we treated each possible kernel as a different classifier, with its own set of hyperparameters: Linear(4), RBF(5), Polynomial(7), and Sigmoid(6).

In total, our parameterization had 65 hyperparameters: 6 for preprocessing and 53 for classification.
The search space includes 15 boolean variables, 14 categorical, 17 discrete, and 19 real-valued variables.
Although the total number of hyperparameters is large, the number of {\em active} hyperparameters describing any one model is much smaller: a model consisting of \texttt{PCA} and a \texttt{RandomForest} for example,
would have only 12 active hyperparameters (1 for the choice of preprocessing, 2 internal to PCA, 1 for the choice of classifier and 8 internal to the RF).
Hyperopt description language allows us to differentiate between {\em conditional} hyperparameters (which must always be assigned) and {\em non-conditional} hyperparameters (which may remain unassigned when they would be unused).
We make use of this mechanism extensively so that Hyperopt's search algorithms do not waste time learning by trial and error that e.g. RF hyperparameters have no effect on SVM performance.
Even internally within classifiers, there are instances of conditional parameters: \texttt{KNN} has conditional parameters depending on the distance metric,
and \texttt{LinearSVC} has 3 binary parameters (``loss'', ``penalty'', and ``dual'') that admit only 4 valid joint assignments.
We also included a blacklist of (preprocessing, classifier) pairs that did not work together, e.g. PCA and MinMaxScaler were incompatible with MultinomialNB, TF-IDF could only be used for text data, and the tree-based classifiers were not
compatible with the sparse features produced by the TF-IDF preprocessor.
Allowing for a 10-way discretization of real-valued hyperparameters, and taking these conditional hyperparameters into account, a grid search of our search space would still require an infeasible number of evalutions (on the order of $10^{12}$).

@@

\begin{figure}
    \centering
    \includegraphics[width=5.00in]{graphics/AverageTestScoresClassifiersTPE}
    \caption{
        For each data set, searching the full configuration space (``Any Classifier'') delivered performance approximately on par with a search that was restricted to the best classifier type.
        (Best viewed in color.)
    }
    \label{fig:avg_test_scores}
%\vspace{-3em}
\end{figure}
